%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Vikas}{Choudhary}
       { Web developer}
       
       

% In the aside, each new line forces a line break
\begin{aside}
  \section{About}
    S-124
    Ravindra Bhawan
    IIT Roorkee
    ~
    {8006622945}
  \section{languages}
    English
   Hindi
   Punjabi
  \section{programming}
    {\color{red} $\varheartsuit$} JavaScript
    Python, C++,CSS3 and HTML5
    
  \section{Softwares}
    {\color{red} $\varheartsuit$} Microsoft Office,
    Adobe photoshop,
    Adobe afterEffects,
    Cinema 4-d.
    
    \section{Links}
    {\color{red} $\varheartsuit$} 
    Github://kickas
    LinkedIn://kickas
    
    
\end{aside}
\section{}


\entry 
    {\emph{"Currently an undergraduate at Indian Institute of Technology Roorkee.Seeking for Practical work experience as a web developer.Looking to start my career in web development in a role where I can build  something on the skills gained at university and through various online platforms."}}






\section{Education}

\begin{entrylist}
  \entry
    {Since 2014}
    {B.Tech. {\normalfont Indian Institute Of Technology}}
    {Ongoing}
    {\emph{Candidate of Materials Engineering.}}
  \entry
    {2013–2014}
    {AISSCE,12 {\normalfont  CBSE}}
    {Percentage:90.4}
    {With Physics,Chemistry,Maths}
  \entry
    {2011–2012}
    {AISSE,10 {\normalfont  CBSE}}
    {Grade:10}
 
\end{entrylist}


\section{Additional Education}

\begin{entrylist}
    \entry
    {2014}
    {Edx}
    
    {CS-50,Intro to computer science}
    
   \entry
    {2014-16}
    {Codecademy}
    
    {HTML,CSS,Javascript,Python,Jquery,SQL}
    \entry
    {2016-pres.}
    {TreeHouse}
    
    {AJAX Basics,Jquery bascis}
 
  \entry
    {2015-pres.}
    {Udemy}
     
   { {The Complete Python Programming Course (2015),}
  
    {The web-developer bootcamp,- Projects in CSS}}
\end{entrylist}


\section{Personal projects}


\entry
    
    {Oreva}
     
    {\emph{An ovverride new tab-extension is made by fetching Data from different API's on every refresh by using AJAX.}}
    \entry
    
    {Color-game}
    
    {\emph{The purpose is to enhance  the knowledge of the concept of RGB colors.}}
    
    \entry
    
    {Image slider}
   
    {\emph{Using HTML,CSS,JS and Jquery image slider is made. }}
    
    \entry
    
    {Animated android app logo}
 
    {\emph{Simple animations are made by using Css animations tags -transform and -transision.}}

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
